\documentclass[a4paper]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{geometry}
\geometry {
 a4paper,
 left=20mm,
 right=20mm,
 top=20mm,
 bottom=10mm,
}
\textheight=9in
\raggedbottom
\raggedright

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME

\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder}
\newcommand{\employer}[4]{{ \textbf{#1} #2  (#3).\\ \underline{\emph{#4}}\\  }}
\newcommand{\contact}[3]{
\vspace*{-8pt}
\begin{center}
{\LARGE \scshape {#1}}\\
#2 \lineunder
#3
\end{center}
\vspace*{-8pt}
}
\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}}

\newcommand{\school}[3]{
 \textbf{#1} #2 \\\vspace*{3pt} #3\\
\vspace*{5pt}
}

% END RESUME DEFINITIONS

\begin{document}

\small
\smallskip
\contact{Chaitanya Dandugula}
{Bangalore - 560074}
{Mob: \textbf{+91-6363493863} $\bullet$ Email: \textbf{hireme@chadan.in}}
\vspace*{5pt}

\header{Summary}
Telecommunication Engineer with expertise in C and C++ programming with more than 8 years of design and development experience. Familiarity with software development in Java, Python, Scala etc.

Domain knowledge in Bluetooth, IVR applications and networking applications.

\header{Skills}
\begin{achievements}
\item Proficiency in software development in C, C++ with more than 8 years of experience.
\item Proficiency with GNU/Linux development environment with more than 8 years of experience.
\item Solid understanding of object oriented analysis, design and programming.
\item Strong debugging/troubleshooting skills.
\item Proficient in Multi-threading programming.
\item Proficient with network monitoring tools like Wireshark and Nmap.
\item Familiarity in software development in Java, Python and Scala.
\item Familiarity with mathematical tools like MATLAB and Mathematica.
\item Familiarity with SQL, git, valgrind and debuggers(gdb / MS-VS debugger)
\item Limited exposure to Flask and MongoDB.
\end{achievements}

\header{Related Work Experience}
\employer{Infinera} {Bangalore, \textit{India}} {December 2017 - Present} {Lead Engineer}
	\begin{achievements}
          \item Developing optical chassis simulator. 
          \item Developing features for control plane on the optical networking element.
          \item Working on implementing intelligent L2 switching.
          \item Technologies: Linux, Broadcom SDK.
	\end{achievements}

\employer{Actiance} {Bangalore, \textit{India}} {8 Months} {System Analyst}
	\begin{achievements}
          \item Contributed towards building a recording solution- AMR (composed of 8 modules) for Skype for Business.
          \item Took ownership of the very unstable and buggy STUN module and made it one of the stable components within 6 months.
          \item Worked closely with the performance team to imporve the overall performance of AMR (both in terms of memory footprint and execution speed).
          \item Technologies: SIP, STUN, Skype for business front-end server.
	\end{achievements}

\employer{Unified Messaging Systems} {Bangalore, \textit{India}} {4 Years} {Senior Developer}
	\begin{achievements}
	  \item Primary responsibilities includes the design, development and testing of additional components of the back-end system for sending out voice alerts (IVR application).
	  \item Contributed to all phases of the software design along with the technical architect team.
	  \item Design, development and testing of a call processing library to interface with Dialogic HMP (E1/T1 telecom cards) platform.
	  \item Design, development and testing of a voice conference application from the ground up.
	  \item Monitoring and resolving issues related to the production setup of the back-end system.
	  \item Worked on advanced C++ design patterns like policy based class design, command objects and object factories.
	  \item Extensive usage of the C++ STL \& Boost libraries (Multithreading, Containers, etc) across all projects.
	  \item Extensive usage of SQL (MS-SQL) in all the projects.
	  \item Developed Python scripts for Database monitoring on the production environment.
	  \item Provided inputs to the business development team during the product specification review.
	  \item Assisted sales team in better time estimation of the various deliverables (software).
	  \item Working with a distributed team across different geographies.
	\end{achievements}

\break
\employer{Fraunhofer Research Institution for Applied and Integrated Security} {Munich, \textit{Germany}} {6 Months}{Student Research Assistant}
	\begin{achievements}
	  \item Master thesis project - ``Networking for smart meters"
	  \item Evaluation of different network architectures suitable for building a network between a smart meter and a gateway.
	  \item Evaluation of different network security protocols suitable for the network.
          \item Technologies - TCP, UDP, HIP, IP over transmission lines.
	\end{achievements}

\employer{Kungliga Tekniska H\"{o}gskolan}{Stockholm, \textit{Sweden}}{5 Months}{Tech Lead}
  \begin{achievements}
    \item Developing the group communication feature in the open source VoIP client - MiniSIP.
    \item Worked as a technical lead of a 5 member International student team.
    \item Implemented the group communication feature in the SIP core library of Minisip.
    \item Re-designed the Minisip GTK GUI for group communication feature.
    \item Technologies – C/C++, SIP, RTP, i2conf, audio codecs.
    \item \href{https://archive.ssvl.kth.se/csd2010/csd.xen.ssvl.kth.se/csdlive/content/salcas.html}{Project website} - \ 
	  \href{https://github.com/dandugula/minisip_salcas}{Git repository}.
  \end{achievements}

\employer{Nokia Siemens Networks}{Helsinki, \textit{Finland}}{3 Months}{Summer Trainee}
	\begin{achievements}
          \item Part of the Flexiplatform IP Networking team.
	  \item CPP Unit testing of the IPSec module of Flexiplatform\footnote[1]{A proprietary OS for base station hardware from NSN.}.
	  \item Setting up of complex networking scenarios using AdvancedTCA (ATCA) blades for testing of IPSec.
	  \item Setting up of a development server, for my team, based on RHEL and a custom software development toolchain for WindRiver Linux platform.
	  \item Worked in a Agile software development environment.
	\end{achievements}

\employer{MindTree} {Bangalore, \textit{India}}{2 Years} {Software Engineer}
	\begin{achievements}
	\item Design and implementation of Bluetooth profiles and protocols for EtherMind\footnote[2]{A proprietary Bluetooth stack of MindTree Ltd.}.
	\item Porting of EtherMind to various embedded systems with proprietary RTOS.
	\item Integration of Audio codecs with the Bluetooth stack.
	\item Auditing of security aspects of Bluetooth enabled devices.
	\item Bluetooth conformance testing with PTS and FTS tools.
	\item Development of scripts in Python for automated code-formatting.
	\end{achievements}

\header{Education}

\school{Kungliga Tekniska H\"{o}gskolan}{Stockholm, \textit{Sweden}.}
{Master of Science - Communication Systems, 2012}

\school{P.E.S Institute of Technology, Visveswaraiah Technological University}{Bangalore, \textit{India}.}{Bachelor of Engineering - Telecommunication Engineering, 2007}

\break
\header{Other Work Experience}
\employer{Narlax Info Systems} {Bangalore, \textit{India}}{1 Month}{Instructor}
	\begin{achievements}
	\item Taught ``Algorithms and Data Structures" course for final year B.E students.
	\end{achievements}

\employer{Youth for Seva}{Bangalore, \textit{India}}{2 Years}{Volunteer}
\begin{achievements}
\item Helped a team of doctors in conducting medical chekup camps at Govt. primary schools across Bangalore.
\item Lead a team of 5 volunteers in organizing hospital visit drives for the Govt. schools students.
\item Lead a team of 15 volunteers in planning and organizing an inter-school cultural festival - `Chiguru'(participants: \textasciitilde 1500)
\item Volunteered for various activities of Youth for Seva in Education and health care divisions.
\end{achievements}

\employer{Beta Labs Pvt. Ltd.}{Bangalore, \textit{India}}{3 Months}{Technical Director}
\begin{achievements}
\item Co-founded `Semester-9' - a unique education program to connect the fresh Engineering graduates to the start up community.
\item Formulated a 3-month go-to market plan.
\item Setup the website and the course syllabus.
\item Marketed the idea to 5 Engineering colleges with around 250 students.
\item Marketed the idea to startup incubators (Microsoft Accelerator, Open Coffee Club) and bought a few early stage startups on board.
\end{achievements}

\header{Publication}
\begin{achievements}
\item  Deepak M Subramanian, \emph{Chaitanya Dandugula}, Deepak Kumar, Jayanth V and Karun Ramakrishnan,\textbf{``Intelligent Traffic Controller using image processing Techniques"}, IEEE – INDICON 2007, Bangalore, India.
\end{achievements}

\hspace*{-18pt} \hrulefill \\
\textit{\href{http://se.linkedin.com/in/dandugula}{LinkedIn profile}}.\\
\end{document}
